The Importance of Affective States in Privacy Calculus

### 2021-05-02 submission.tex
findings on social media

\subsection{VPN Usage}
We exclude from our analyses one respondent who did not know what a VPN was.

>>>>

A strong relationship exists between \emph{the proportion of social media for
which an individual has set up privacy settings and how they feel when they are
setting up those settings}, with a correlation of magnitude .742. This
relationship is highly significant (p<.01, **). Despite the a relatively low
Chi-Square (p=.115), we cannot rule out the null hypothesis.

\subsection{ISP Tracking Concerns and VPN Usage}
We exclude from our analyses one respondent who did not know what a VPN was.
